Affective Uplift During Video Game Play: A Naturalistic Case Study

### 2024-04-04 ms.Rmd
Fixes to reproducibility

# Convert types and units
dat <- dat |>
  mutate(
    pid = factor(pid),
    # Mood to 0-1 scale
    mood = mood / 1000,
    # hours indicates session duration in hours
    hours = duration / 60,
    .keep = "unused"
  )
```

```{r}
#| label: session-indicator-create
#| include: true

dat <- dat |>
  arrange(pid, time) |>
  mutate(
    new_session = hours < lag(hours, default = 999),
    session = cumsum(new_session),
    .by = pid
  ) |>
  select(-c(new_session)) |>
  mutate(ps = paste(pid, session, sep = "_"))

dat_sum <- dat |>
  summarize(
    when = "raw",
    n_pid = length(unique(pid)),
    n_session = length(unique(ps)),
    n_obs = n()
  )
```

```{r}
#| label: mood-filter

@@

dat_sum <- dat |>
  summarize(
    when = "mood",
    n_pid = length(unique(pid)),
    n_session = length(unique(ps)),
    n_obs = n()
  ) |>
  bind_rows(dat_sum)
```

>>>>

# Convert types and units
dat <- dat |>
  mutate(
    pid = factor(pid),
    # Mood to 0-1 scale
    mood = mood / 1000,
    # hours indicates session duration in hours
    hours = duration / 60,
    .keep = "unused"
  )

# Create session indicators
dat <- dat |>
  arrange(pid, time) |>
  mutate(
    new_session = hours < lag(hours, default = 999),
    session = cumsum(new_session),
    .by = pid
  ) |>
  select(-c(new_session)) |>
  mutate(ps = paste(pid, session, sep = "_"))

dat_sum <- dat |>
  summarize(
    when = "raw",
    n_pid = length(unique(pid)),
    n_session = length(unique(ps)),
    n_obs = n()
  )

@@

# Analyze a subset of participants if required 
# (for testing etc.; be careful)
dat <- dat |> 
  filter(
    pid %in%
      sample(
        unique(dat$pid), 
        size = length(unique(dat$pid)) * N_SUBSET_PROPORTION
      )
  )

# Calculate basic data summaries
dat_sum <- dat |>
  summarize(
    when = "mood",
    n_pid = length(unique(pid)),
    n_session = length(unique(ps)),
    n_obs = n()
  ) |>
  bind_rows(dat_sum)
```
